### 2018-12-17 index.Rmd
rebuild site

## Installation
### Installing Dependencies
You should check the [`sf` package website](https://r-spatial.github.io/sf/) for the latest details on installing dependencies for that package. Instructions vary significantly by operating system. For best results, have `sf` installed before you install `areal`. Other dependencies, like `dplyr`, will be installed automatically with `areal` if they are not already present.

The one exception here is the dependency `lwgeom`, which Linux users will need to follow some [spatial instructions](https://github.com/r-spatial/lwgeom) to install correctly.

### Installing areal
The development version of `areal` can be accessed from Github with `remotes`:

```r
# install.packages("remotes")
remotes::install_github("slu-openGIS/areal")
```

>>>>

## Resources
* The [Get started](/areal/) article has:
    * a quick overview of getting up and running with `areal` including **installation tips**,
    * some notes on **preparing data** for interpolation,
    * a brief introduction to the **`aw_interpolate()` function**,
    * tips for **getting help**, **submitting feedback**, 
    * and the `areal` package's development roadmap!
* Additional details about preparing data are available in a [dedicated article](/data-preparation/).
* The areal weighted interpolation process is described in-depth in a [dedicated article](/areal-weighted-interpolation/).
